### 2014-10-09 writing/AAAI SSS '15/methods.tex
Revised wordnet section
Trimming methods.

% TODO: Should we cite our NIPS manuscript?

@@

@@

For a comparison funtion, we evaluate versions of the model with both
a plain NN and the NTN layer function proposed in
\citet{chen2013learning}, which adds a third order tensor parameter to
mediate multiplicative interactions between the two inputs. A leaky
ReLU nonlinearity \cite{maasrectifier} is applied to the output of
either layer function.
%
\begin{gather} \label{rnn}
\vec{y}_{\textit{NN}} = f(\mathbf{M} [\vec{x}^{(l)}; \vec{x}^{(r)}] + \vec{b}) ~~~~~~~~~~~~~~~ \vec{y}_{\textit{NTN}} = f(\vec{x}^{(l)T} \mathbf{T}^{[1 \ldots n]} \vec{x}^{(r)} + \mathbf{M} [\vec{x}^{(l)}; \vec{x}^{(r)}] + \vec{b})
\end{gather} 
%

This model differs from that of \citet{Bowman:Potts:Manning:2014} in
two ways. Because the inputs are single symbols, there is no need for
the composition functions used in that (and prior) work. Also, for our
experiment on WordNet data, we introduce an additional neural network
layer between the embedding input and the comparison function, which
facilitates initializing the embeddings themselves from pretrained
vectors and was found to help peformance in that setting.

>>>>

@@

The simpler version of the comparison simply concatenates the two input
vectors before feeding them into a standard neural network (NN) layer.
The more powerful neural tensor network (NTN) version uses an additional 
third-order tensor parameter to allow for multiplicative
interactions between the two inputs. For more details on the implementation and
training of the layer functions, see \cite{Bowman:Potts:Manning:2014}.

@@

This model used here differs from the one described in that work in
two ways. Because the inputs are single symbols, we do not use
a composition function here. Also, for our experiment on WordNet data, 
we introduce an additional neural network layer between the embedding 
input and the comparison function, which facilitates initializing the 
embeddings themselves from pretrained vectors and was found to help 
peformance in that setting.
